### 2018-08-16 doc/paper.tex
Doing initial dump from `phd-thesis`.

\documentclass[letterpaper,10pt]{article}

\usepackage[margin=1in]{geometry}

\usepackage{amsthm,amssymb,amsmath}
\usepackage{bm}
%% H/T: https://tex.stackexchange.com/a/28334/32270
\usepackage{chngcntr}
\counterwithin{equation}{section}
%% H/T: https://tex.stackexchange.com/a/71153/32270
\usepackage[nottoc,notlot,notlof]{tocbibind}

\usepackage[usenames, dvipsnames]{color}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=MidnightBlue,
  citecolor=ForestGreen,
  pdfinfo={
    CreationDate={D:20180816104534},
    ModDate={D:20180816104534},
  },
}

\usepackage{embedfile}
\embedfile{\jobname.tex}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{A Curious Case of Curbed Condition}
\rhead{Danny Hermes}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\qed}{\(\blacksquare\)}
\newcommand{\reals}{\mathbf{R}}
\newcommand{\bigO}[1]{\mathcal{O}\left(#1\right)}
\newcommand{\eps}{\varepsilon}

\begin{document}

\begin{abstract}
\noindent We present a short note describing a condition number
of the intersection of two B\'{e}zier curves. Since tangent
intersections are to transversal intersections as multiple roots are
to simple roots of a function, this condition number is infinite
for non-transveral intersections.
\\ \\
\noindent \textit{Keywords}: B\'{e}zier curve, Curve intersection,
Condition number
\end{abstract}

\tableofcontents

\section{Introduction}

Placeholder

\section{Problem conditioning}\label{sec:conditioning}

Consider a smooth function \(F: \reals^n \longrightarrow \reals^n\)
with Jacobian \(F_{\bm{x}} = J\). We want to consider a special class of
functions of the form \(F\left(\bm{x}\right) = \sum_j c_j
\phi_j\left(\bm{x}\right)\) where the basis
functions \(\phi_j\) are also smooth functions on \(\reals^n\)
and each \(c_j \in \reals\). We want to consider the effects on a root
\(\bm{\alpha} \in \reals^n\) of a perturbation in one of the
coefficients \(c_j\). We examine the perturbed functions
\begin{equation}
G(x, \delta) = F\left(\bm{x}\right) + \delta \phi_j\left(\bm{x}\right).
\end{equation}
Since \(G\left(\bm{\alpha}, 0\right) = \bm{0}\), if \(J^{-1}\) exists at
\(\bm{x} = \bm{\alpha}\) then
the implicit function theorem tells us that we can define
\(\bm{x}\) via
\begin{equation}
G\left(\bm{x}\left(\delta\right), \delta\right) = \bm{0}.
\end{equation}
Taking the derivative with respect to \(\delta\) we find that
\(\bm{0} = G_{\bm{x}} \bm{x}_{\delta} + G_{\delta}\). Plugging in
\(\delta = 0\) we find that \(0 = J\left(\bm{\alpha}\right) \bm{x}_{\delta} +
\phi_j\left(\bm{\alpha}\right)\), hence we
conclude that
\begin{equation}
\bm{x}\left(\delta\right) = \bm{\alpha} - J\left(\bm{\alpha}\right)^{-1}
  \phi_j\left(\bm{\alpha}\right) \delta + \bigO{\delta^2}.
\end{equation}
This gives a relative condition number (for the root) of
\begin{equation}
\frac{\left \lVert J\left(\bm{\alpha}\right)^{-1}
  \phi_j\left(\bm{\alpha}\right) \right \rVert}{
  \left \lVert \bm{\alpha} \right \rVert}.
\end{equation}

By considering perturbations in \emph{all} of the coefficients:
\(\left|\delta_j\right| \leq \eps \left|c_j\right|\), a similar analysis
gives a root function
\begin{equation}
\bm{x}\left(\delta_0, \ldots, \delta_n\right) = \bm{\alpha} -
  J\left(\bm{\alpha}\right)^{-1} \sum_{j = 0}^n \delta_j
  \phi_j\left(\bm{\alpha}\right) + \bigO{\eps^2}.
\end{equation}
With this, we can define a root condition number
\begin{equation}\label{eq:abstract-cond-num}
\kappa_{\bm{\alpha}} =
  \lim_{\eps \to 0} \left(\sup \frac{\left \lVert\delta \bm{\alpha}
  \right \rVert / \eps}{\left \lVert\bm{\alpha}\right \rVert}\right) =
  \lim_{\eps \to 0} \left(\sup \frac{\left \lVert
  J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
  \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
  \left \lVert\bm{\alpha}\right \rVert}\right).
\end{equation}

When \(n = 1\), \(J^{-1}\) is simply \(1 / F'\) and we find
\begin{equation}
\kappa_{\alpha} =
  \frac{1}{\left|\alpha F'(\alpha)\right|} \sum_{j = 0}^n \left|
  c_j \phi_j(\alpha)\right|.
\end{equation}
This value is given by the triangle inequality applied to
\(\delta \alpha\)  and equality can be attained since the sign
of each \(\delta_j = \pm c_j \eps\) can be modified at will to make
\(\phi_j(\alpha) \delta_j = \left|\phi_j(\alpha) c_j\right| \eps\).

When \(n > 1\), the triangle inequality tells us that
\begin{equation}
\kappa_{\bm{\alpha}} =
  \lim_{\eps \to 0} \left(\sup \frac{\left \lVert\delta \bm{\alpha} /
  \eps\right \rVert}{\left \lVert\bm{\alpha}\right \rVert}\right) \leq
  \frac{1}{\left \lVert\bm{\alpha}\right \rVert} \sum_{j = 0}^n
  \left|c_j\right| \left \lVert J\left(\bm{\alpha}\right)^{-1}
  \phi_j(\bm{\alpha})\right \rVert.
\end{equation}
However, this bound is only attainable if all
\(\phi_j(\bm{\alpha})\) are parallel. However, we'll seldom need to
compute the exact condition number and are instead typically
interested in the order of magnitude. In this case a lower
bound
\begin{equation}
\frac{1}{\left \lVert\bm{\alpha}\right \rVert}
\max_j \left|c_j\right| \left \lVert J\left(\bm{\alpha}\right)^{-1}
\phi_j(\bm{\alpha})\right \rVert
\end{equation}
for \(\kappa_{\bm{\alpha}}\)
will suffice as an approximate condition number.

For an example, consider
\begin{equation}
\phi_0 = \left[ \begin{array}{c} x_0 \\ 2 \\ 0 \end{array}\right],
\phi_1 = \left[ \begin{array}{c} 0 \\ x_1 \\ 3 \end{array}\right],
\phi_2 = \left[ \begin{array}{c} 2 \\ 0 \\ x_2 \end{array}\right],
F = \phi_0 + 2 \phi_1 + 3 \phi_2,
\bm{\alpha} = \left[ \begin{array}{c} -6 \\ -1 \\ -2 \end{array}\right].
\end{equation}
For a given \(\eps\), the maximum root perturbation occurs when
\(\delta_0 = \eps, \delta_1 = 2 \eps, \delta_2 = -3 \eps\) and
gives
\(\left \lVert J\left(\bm{\alpha}\right)^{-1} \sum_j
\delta_j \phi_j\left(\bm{\alpha}\right) \right \rVert
= 4 \sqrt{10} \eps \approx 12.65 \eps\).
The pessimistic triangle inequality bound gives
\(\sum_j \left|c_j\right| \left \lVert J\left(\bm{\alpha}\right)^{-1}
\phi_j(\bm{\alpha})\right \rVert \approx 14.64 \eps\) and the
maximum individual perturbation is \(2 \sqrt{10} \eps \approx 6.325 \eps\)
(this occurs when \(\delta_0 = \delta_1 = 0, \delta_2 = \pm 3 \eps\)).

In this general framework, we can define a condition number both
for a simple root of a polynomial in Bernstein form and for the
intersection of two planar B\'{e}zier curves. For the first,
\(\phi_j(s) = \binom{n}{j} (1 - s)^{n - j} s^j\) the Bernstein basis
functions, a polynomial \(p(s) = \sum_j b_j \phi_j(s)\) with
a simple root \(\alpha \in \left(0, 1\right]\) has root condition number
\begin{equation}
\kappa_{\alpha} =
  \frac{1}{\alpha \left|p'(\alpha)\right|} \sum_{j = 0}^n \left|
  b_j \phi_j(\alpha)\right| = \frac{\widetilde{p}(\alpha)}{
  \alpha \left|p'(\alpha)\right|}.
\end{equation}
For the intersection of a degree \(m\) curve \(b_1(s)\) and
a degree \(n\) curve \(b_2(t)\), we have basis functions
\begin{multline}
\phi_{0, -1, 1} = \left[ \begin{array}{c} B_{0, m}(s) \\ 0 \end{array}\right],
\phi_{0, -1, 2} = \left[ \begin{array}{c} 0 \\ B_{0, m}(s) \end{array}\right],
\cdots, \\
\phi_{m, -1, 1} = \left[ \begin{array}{c} B_{m, m}(s) \\ 0 \end{array}\right],
\phi_{m, -1, 2} = \left[ \begin{array}{c} 0 \\
  B_{m, m}(s) \end{array}\right], \\
\phi_{-1, 0, 1} = \left[ \begin{array}{c} -B_{0, n}(t) \\
  0 \end{array}\right],
\phi_{-1, 0, 2} = \left[ \begin{array}{c} 0 \\
  -B_{0, n}(t) \end{array}\right], \cdots, \\
\phi_{-1, n, 1} = \left[ \begin{array}{c} -B_{n, n}(t) \\
  0 \end{array}\right], \phi_{-1, n, 2} = \left[ \begin{array}{c} 0 \\
  -B_{n, n}(t) \end{array}\right].
\end{multline}
Since \(F(s, t) = b_1(s) - b_2(t)\) we have Jacobian \(J(s, t) =
\left[ \begin{array}{c c} b_1'(s) & -b_2'(t) \end{array}\right]\). We'll
consider a transversal intersection \(F(\alpha, \beta) = \bm{0}\) with
\(\det J(\alpha, \beta) \neq 0\). Since each of the
\(\phi_j\) is just a scalar multiple of the standard basis
vectors, writing \(J^{-1} = \left[ \begin{array}{c c}
\bm{v}_1 & \bm{v}_2 \end{array}\right]\), we have
\begin{multline}
J\left(\alpha, \beta\right)^{-1} \sum_{\bm{j}} \delta_{\bm{j}}
  \phi_{\bm{j}}\left(\alpha, \beta\right) = \left[\sum_{i = 0}^m
  \delta_{i, -1, 1} B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
  \delta_{-1, j, 1} B_{j, n}\left(\beta\right)\right] \bm{v}_1 \\
+ \left[\sum_{i = 0}^m
  \delta_{i, -1, 2} B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
  \delta_{-1, j, 2} B_{j, n}\left(\beta\right)\right] \bm{v}_2 =
  \nu_1 \bm{v}_1 + \nu_2 \bm{v}_2.
\end{multline}
where
\begin{equation}\label{eq:nu-bounds}
\left|\nu_k\right| / \eps \leq \sum_{i = 0}^m
  \left|c_{i, -1, k}\right| B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
  \left|c_{-1, j, k}\right| B_{j, n}\left(\beta\right) = \mu_k
\end{equation}
and the bound can be attained for both \(k = 1, 2\) by making the
signs of the \(\delta_{\bm{j}}\) agree. If we name the components of each
curve via
\(b_1(s) = \left[ \begin{array}{c c} x_1(s) & y_1(s) \end{array}\right]^T\)
and \(b_2(t) = \left[ \begin{array}{c c} x_2(t) & y_2(t) \end{array}\right]^T\)
then we see that \(\mu_1 = \widetilde{x}_1(\alpha) + \widetilde{x}_2(\beta)\)
and \(\mu_2 = \widetilde{y}_1(\alpha) + \widetilde{y}_2(\beta)\).
Thus we have condition number
\begin{align}
\kappa_{\alpha, \beta} &= \frac{1}{\sqrt{\alpha^2 + \beta^2}}
  \max_{\left|\nu_k\right| \leq \mu_k} \left \lVert \nu_1 \bm{v}_1 +
  \nu_2 \bm{v}_2 \right \rVert_2 \\
  &=
  \sqrt{\frac{\max_{\left|\nu_k\right| \leq \mu_k}
  \nu_1^2 \left(\bm{v}_1 \cdot \bm{v}_1\right) +
  2 \nu_1 \nu_2 \left(\bm{v}_1 \cdot \bm{v}_2\right) +
  \nu_2^2 \left(\bm{v}_2 \cdot \bm{v}_2\right)}{\alpha^2 + \beta^2}}
  \label{eq:intersect-cond-num}.
\end{align}
Since \(J^{-1}\) is invertible, we know \(\bm{v}_1\) and \(\bm{v}_2\) are
not parallel which can be used to show that the only internal critical
point of the function to be maximimized in~\eqref{eq:intersect-cond-num}
is \(\nu_1 = \nu_2 = 0\), which is the global minimum. Along the boundary of
the rectangle
\(\left[-\mu_1, \mu_1\right] \times \left[-\mu_2, \mu_2\right]\),
we fix one of \(\nu_1\) or \(\nu_2\) and the resulting univariate function is
an up-opening parabola, hence any critical point must be a local
minimum. Thus we know the maximum occurs at two of the four corners of the
rectangle:
\begin{equation}\label{eq:intersect-cond-num-too}
\kappa_{\alpha, \beta} = \sqrt{\frac{\mu_1^2
  \left(\bm{v}_1 \cdot \bm{v}_1\right) +
  2 \mu_1 \mu_2 \left|\bm{v}_1 \cdot \bm{v}_2\right| +
  \mu_2^2 \left(\bm{v}_2 \cdot \bm{v}_2\right)}{\alpha^2 + \beta^2}}.
\end{equation}

As far as the author can tell,
a condition number for the intersection of two planar B\'{e}zier curves
has not been described in the Computer Aided Geometric Design (CAGD)
literature. In \cite[Chapter~25, Equation 25.11]{Higham2002}
a more generic condition number is defined for the root of a nonlinear
algebraic system that is similar to the definition above.

For an example, consider the line
\(b_1(s) = \left[ \begin{array}{c c} 2s & 2s \end{array}\right]^T\)
and improperly parameterized line
\(b_2(t) = \left[ \begin{array}{c c} 4t^2 & 2 - 4t^2
\end{array}\right]^T\) which intersect at \(\alpha = \beta = 1/2\).
At the intersection we have \(J^{-1} = \frac{1}{8}
\left[ \begin{array}{c c} 2 & 2 \\ -1 & 1 \end{array}\right]\),
so that \(\bm{v}_1 \cdot \bm{v}_1 = \bm{v}_2 \cdot \bm{v}_2 =
5/64\) and \(\bm{v}_1 \cdot \bm{v}_2 = 3/64\). Since the
\(x\)-component of \(F(s, t)\) can be written as
\(2s - 4t^2 = 2 B_{1, 1}(s) - 4 B_{2, 2}(t)\) and the
\(y\)-component as \(2s + 4t^2 - 2 = 2 B_{1, 1}(s) - 2 B_{0, 2}(t)
- 2 B_{1, 2}(t) + 2 B_{2, 2}(t)\) we have
\begin{alignat}{2}
\mu_1 &= 2 B_{1, 1}(\alpha) &&+ 4 B_{2, 2}(\beta) = 2 \\
\mu_2 &= 2 B_{1, 1}(\alpha) + 2 B_{0, 2}(\beta) +
  2 B_{1, 2}(\beta) &&+ 2 B_{2, 2}(\beta) = 3.
\end{alignat}
Following~\eqref{eq:intersect-cond-num-too}, this gives
\(\kappa_{\alpha, \beta} = \sqrt{202}/8 \approx 1.78\).

\bibliography{paper}
\bibliographystyle{alpha}

\end{document}

### 2018-08-16 nox.py

@@ -1,0 +1,82 @@
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+#     https://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+"""This is a configuration file for running ``nox`` on this project.
+
+To determine the supported actions run ``nox --list-sessions`` from the
+project root.
+"""
+
+import os
+
+import nox
+import py.path
+
+
+NOX_DIR = os.path.abspath(os.path.dirname(__file__))
+SINGLE_INTERP = "python3.7"
+
+
+def get_path(*names):
+    return os.path.join(NOX_DIR, *names)
+
+
+class Remove(object):
+    def __init__(self, prefix, extensions):
+        self.prefix = prefix
+        self.extensions = extensions
+
+    def __call__(self):
+        for extension in self.extensions:
+            path = "{}.{}".format(self.prefix, extension)
+            os.remove(path)
+
+
+def build_tex_file(session, base, new_id, extensions=()):
+    # NOTE: This assumes that ``session.chdir(get_path('doc'))``
+    #       has been called.
+    modify_id = get_path("scripts", "modify_pdf_id.py")
+
+    session.run("pdflatex", base)
+    session.run("bibtex", base)
+    session.run("pdflatex", base)
+    session.run("bibtex", base)
+    session.run("pdflatex", base)
+    session.run("pdflatex", base)
+
+    path = get_path("doc", base)
+    remove = Remove(path, extensions)
+    session.run(remove)
+    session.run("python", modify_id, "--base", path, "--id", new_id)
+
+
+@nox.session
+def build_tex(session):
+    session.interpreter = SINGLE_INTERP
+
+    if py.path.local.sysfind("pdflatex") is None:
+        session.skip("`pdflatex` must be installed")
+
+    if py.path.local.sysfind("bibtex") is None:
+        session.skip("`bibtex` must be installed")
+
+    # No need to create a virtualenv.
+    session.virtualenv = False
+
+    session.chdir(get_path("doc"))
+
+    build_tex_file(
+        session,
+        "paper",
[…]

### 2018-08-18 doc/paper.tex
Finishing paper.

@@
 \usepackage{amsthm,amssymb,amsmath}
+%% https://tex.stackexchange.com/a/396829/32270
+\allowdisplaybreaks
 \usepackage{bm}
@@
 \usepackage[nottoc,notlot,notlof]{tocbibind}
+
+\theoremstyle{definition}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{definition}{Definition}[section]
 
@@
 \pagestyle{fancy}
-\lhead{A Curious Case of Curbed Condition}
+\lhead{A 2-Norm Condition Number for B\'{e}zier Curve Intersection}
 \rhead{Danny Hermes}
@@
 \noindent We present a short note describing a condition number
-of the intersection of two B\'{e}zier curves. Since tangent
-intersections are to transversal intersections as multiple roots are
-to simple roots of a function, this condition number is infinite
-for non-transveral intersections.
+of the intersection of two B\'{e}zier curves.
 \\ \\
-\noindent \textit{Keywords}: B\'{e}zier curve, Curve intersection,
-Condition number
+\noindent \emph{Keywords}: B\'{e}zier curve, Curve intersection,
+Condition number, Numerical analysis
 \end{abstract}
@@
 
-Placeholder
+The problem of intersecting two planar B\'{e}zier curves is an important
+one in Computer Aided Geometric Design (CAGD).
+Many intersection algorithms have been described in the literature, both
+geometric (\cite{Sederberg1986, Sederberg1990, Kim1998}) and algebraic
+(\cite{Manocha:CSD-92-698}). Though the general convergence properties
+of these algorithms have been studied (e.g. \cite{Schulz2009}),
+no condition number for the intersection problem has been described in
+the CAGD literature\footnote{As far as the author has been able to tell.
+In many CAGD textbooks, there is a long review of methods for intersecting
+two planar B\'{e}zier curves (e.g. \cite{Farin2001, SederbergNotes}) but no
+mention of conditioning.}.
 
-\section{Problem conditioning}\label{sec:conditioning}
+There are more generic condition numbers for rational polynomial systems
+(\cite{Herman2015}) or nonlinear algebraic systems
+(\cite[Chapter~25, Section 25.4]{Higham2002}). However, the condition
+numbers with an algebraic focus (rather than an analytic one) often
+require too much computation to be useful. The numerical analytic condition
+numbers are in some ways too general to be useful for planar B\'{e}zier
+curve intersection.
+
+In this paper, we describe a simple relative root condition number for this
+intersection problem. Since tangent intersections are to transversal
+intersections as multiple roots are to simple roots of a function, this
+condition number is infinite for non-transversal intersections.
+We present a few examples verifying that the condition number increases as
+a family of intersections approach an ill-behaved intersection.
+
+\section{Preliminaries}
+
+Throughout, we'll refer to a \emph{B\'{e}zier curve} as a parametric
+plane curve given by
+\begin{equation}
+b(s) = \sum_{j = 0}^n \bm{b}_j B_{j, n}(s)
+\end{equation}
+where \(B_{j, n}(s) = \binom{n}{j} (1 - s)^{n - j} s^j\) is a Bernstein
+polynomial.
+When the parameter \(s \in \left[0, 1\right]\), the coefficients
+\(B_{j, n}(s) \in \left[0, 1\right]\) as well and the evaluation is a convex
+combination of the set of \emph{control points} \(\bm{b}_j \in \reals^2\).
+
+A B\'{e}zier curve intersection is a root \(\left[\begin{array}{c}
+\alpha \\ \beta \end{array}\right]\) of the function
+\begin{equation}
+F(s, t) = b_0(s) - b_1(t)
+\end{equation}
+where \(b_0(s)\) and \(b_1(t)\) are B\'{e}zier curves. Note that
+\(F: \reals^2 \longrightarrow \reals^2\).
+
+Each component \(x(s)\) and \(y(s)\) of a B\'{e}zier curve is a
+polynomial in Bernstein form. For such a polynomial
+\begin{equation}
+p(s) = \sum_{j = 0}^n p_j B_{j, n}(s)
+\end{equation}
+the (absolute) condition number of evaluation is
+\(\widetilde{p}(s) = \sum_{j = 0}^n \left|p_j\right| B_{j, n}(s)\)
+(\cite{Farouki1987}) when the parameter \(s\) is in the unit interval.
+
+\section{Conditioning of Generic Root-finding}
 
@@
 \(\bm{\alpha} \in \reals^n\) of a perturbation in one of the
-coefficients \(c_j\). We examine the perturbed functions
+coefficients \(c_j\). We examine the perturbed function
 \begin{equation}
@@
 \end{equation}
-This gives a relative condition number (for the root) of
+This gives
 \begin{equation}
@@
 \end{equation}
-
+as the relative condition number for a perturbation in \(c_j\).
 By considering perturbations in \emph{all} of the coefficients:
@@
 With this, we can define a root condition number
-\begin{equation}\label{eq:abstract-cond-num}
+
+\begin{definition}\label{defn:abstract-cond-num}
+For a smooth function \(F\left(\bm{x}\right) = \sum_j c_j
+\phi_j\left(\bm{x}\right)\) parameterized by the coefficients
+\(\left\{c_j\right\}\) with root \(\bm{\alpha}\) and Jacobian
+\(J\left(\bm{\alpha}\right)\), we define a relative root condition
+number
+\begin{equation}
 \kappa_{\bm{\alpha}} =
-  \lim_{\eps \to 0} \left(\sup \frac{\left \lVert\delta \bm{\alpha}
-  \right \rVert / \eps}{\left \lVert\bm{\alpha}\right \rVert}\right) =
-  \lim_{\eps \to 0} \left(\sup \frac{\left \lVert
+  \limsup_{\eps \to 0} \frac{\left \lVert\delta \bm{\alpha}
+  \right \rVert / \eps}{\left \lVert\bm{\alpha}\right \rVert} =
+  \lim_{\eps \to 0} \left(\sup_{\left|\delta_j\right| \leq
+  \eps \left|c_j\right|} \frac{\left \lVert
   J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
@@
 \end{equation}
+\end{definition}
 
-When \(n = 1\), \(J^{-1}\) is simply \(1 / F'\) and we find
+In \cite[Chapter~25, Section 25.4]{Higham2002} a similar definition is
+given. Instead of bounding the perturbations component-wise, it bounds
+the entire perturbation vector
+\begin{equation}
+  \lim_{\eps \to 0} \left(\sup_{\left \lVert \bm{\delta} \right \rVert \leq
+  \eps \left \lVert \bm{c} \right \rVert} \frac{\left \lVert
+  J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
+  \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
+  \left \lVert \bm{\alpha} \right \rVert}\right) =
+  \left \lVert J^{-1} F_{\bm{c}} \right \rVert \frac{\left \lVert \bm{c}
+  \right \rVert}{\left \lVert \bm{\alpha} \right \rVert}.
+\end{equation}
+While this has the benefit of having a closed form that is straightforward
+to compute, it may be less useful than the condition number given in
+Definition~\ref{defn:abstract-cond-num} since the larger coefficients
+can dominate the rest.
+
+\subsection{One-dimensional Case}
+
+When \(n = 1\), due to the triangle inequality:
+\begin{equation}\label{eq:tri-ineq}
+\left|\delta \alpha\right| = \left|J^{-1} \sum_{j = 0}^n
+  \delta_j \phi_j(\alpha)\right| \leq \frac{1}{\left|F'(\alpha)\right|}
+  \sum_{j = 0}^n \left|\delta_j \phi_j(\alpha)\right|.
+\end{equation}
+The sign and magnitude of each \(\delta_j\) can be chosen to make
+\(\delta_j \phi_j(\alpha) = \left|c_j \phi_j(\alpha)\right| \eps\),
+hence for these values equality holds in the triangle inequality:
+\begin{equation}
+\left|\sum_{j = 0}^n \delta_j \phi_j(\alpha)\right| =
+\eps \sum_{j = 0}^n \left|c_j \phi_j(\alpha)\right|.
+\end{equation}
+Thus we get a root condition number for a polynomial given in Bernstein form
 \begin{equation}
@@
 \end{equation}
-This value is given by the triangle inequality applied to
-\(\delta \alpha\)  and equality can be attained since the sign
-of each \(\delta_j = \pm c_j \eps\) can be modified at will to make
-\(\phi_j(\alpha) \delta_j = \left|\phi_j(\alpha) c_j\right| \eps\).
+that agrees with the common definition (\cite{Farouki1987}) when the
+\(\phi_j\) are specialized to Bernstein basis functions.
 
-When \(n > 1\), the triangle inequality tells us that
+\section{Conditioning of B\'{e}zier Curve Intersection}
+
+To define a condition number for the intersection of two planar B\'{e}zier
+curves, we write the difference as
 \begin{equation}
-\kappa_{\bm{\alpha}} =
-  \lim_{\eps \to 0} \left(\sup \frac{\left \lVert\delta \bm{\alpha} /
-  \eps\right \rVert}{\left \lVert\bm{\alpha}\right \rVert}\right) \leq
-  \frac{1}{\left \lVert\bm{\alpha}\right \rVert} \sum_{j = 0}^n
-  \left|c_j\right| \left \lVert J\left(\bm{\alpha}\right)^{-1}
-  \phi_j(\bm{\alpha})\right \rVert.
+F(s, t) = \left[ \begin{array}{c} x_0(s) \\ 0 \end{array}\right] +
+  \left[ \begin{array}{c} 0 \\ y_0(s) \end{array}\right] -
+  \left[ \begin{array}{c} x_1(t) \\ 0 \end{array}\right] -
+  \left[ \begin{array}{c} 0 \\ y_1(t) \end{array}\right].
 \end{equation}
-However, this bound is only attainable if all
-\(\phi_j(\bm{\alpha})\) are parallel. However, we'll seldom need to
-compute the exact condition number and are instead typically
-interested in the order of magnitude. In this case a lower
-bound
+We can show that there is a closed form for the condition number given
+by Definition~\ref{defn:abstract-cond-num}, specialized to the
+2-norm.
+
+\begin{theorem}
+Let \(\left[\begin{array}{c} \alpha \\ \beta
+\end{array}\right]\) be a transversal intersection of two planar
+B\'{e}zier curves \(b_0(s)\) and \(b_1(t)\). Define the vectors
 \begin{equation}
-\frac{1}{\left \lVert\bm{\alpha}\right \rVert}
-\max_j \left|c_j\right| \left \lVert J\left(\bm{\alpha}\right)^{-1}
-\phi_j(\bm{\alpha})\right \rVert
+\widetilde{F}_{+} = \left[ \begin{array}{c}
+  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
+  \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta) \end{array}\right] \quad
+\text{and} \quad
+\widetilde{F}_{-} = \left[ \begin{array}{c}
+  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
+  -\widetilde{y}_0(\alpha) - \widetilde{y}_1(\beta)\end{array}\right].
 \end{equation}
-for \(\kappa_{\bm{\alpha}}\)
-will suffice as an approximate condition number.
+Then the root condition number of the intersection is the
+greater of two vector norms:
+\begin{equation}
+\kappa_{\alpha, \beta} = \frac{1}{\sqrt{\alpha^2 + \beta^2}} \max \left\{
+\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{+}\right \rVert_2,
+\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{-}\right \rVert_2
+\right\}.
+\end{equation}
+\end{theorem}
 
-For an example, consider
+\begin{proof}
+Let the curve \(b_0(s)\) be degree \(m\) and \(b_1(t)\) be degree \(n\).
+Then \(F(s, t)\) can be written as \(2(m + 1) + 2(n + 1)\) terms:
 \begin{equation}
-\phi_0 = \left[ \begin{array}{c} x_0 \\ 2 \\ 0 \end{array}\right],
-\phi_1 = \left[ \begin{array}{c} 0 \\ x_1 \\ 3 \end{array}\right],
-\phi_2 = \left[ \begin{array}{c} 2 \\ 0 \\ x_2 \end{array}\right],
-F = \phi_0 + 2 \phi_1 + 3 \phi_2,
-\bm{\alpha} = \left[ \begin{array}{c} -6 \\ -1 \\ -2 \end{array}\right].
+F(s, t) =
+  \sum_{i = 0}^m c_i^{(1)} \left[ \begin{array}{c}
+  B_{i, m}(s) \\ 0 \end{array}\right] +
+  \sum_{i = 0}^m c_i^{(2)} \left[ \begin{array}{c}
+  0 \\ B_{i, m}(s) \end{array}\right] +
+  \sum_{j = 0}^n c_j^{(3)} \left[ \begin{array}{c}
+  -B_{j, n}(t) \\ 0 \end{array}\right] +
+  \sum_{j = 0}^n c_j^{(4)} \left[ \begin{array}{c}
+  0 \\ -B_{j, n}(t) \end{array}\right].
 \end{equation}
-For a given \(\eps\), the maximum root perturbation occurs when
-\(\delta_0 = \eps, \delta_1 = 2 \eps, \delta_2 = -3 \eps\) and
-gives
-\(\left \lVert J\left(\bm{\alpha}\right)^{-1} \sum_j
-\delta_j \phi_j\left(\bm{\alpha}\right) \right \rVert
-= 4 \sqrt{10} \eps \approx 12.65 \eps\).
-The pessimistic triangle inequality bound gives
-\(\sum_j \left|c_j\right| \left \lVert J\left(\bm{\alpha}\right)^{-1}
-\phi_j(\bm{\alpha})\right \rVert \approx 14.64 \eps\) and the
-maximum individual perturbation is \(2 \sqrt{10} \eps \approx 6.325 \eps\)
-(this occurs when \(\delta_0 = \delta_1 = 0, \delta_2 = \pm 3 \eps\)).
-
-In this general framework, we can define a condition number both
-for a simple root of a polynomial in Bernstein form and for the
-intersection of two planar B\'{e}zier curves. For the first,
-\(\phi_j(s) = \binom{n}{j} (1 - s)^{n - j} s^j\) the Bernstein basis
-functions, a polynomial \(p(s) = \sum_j b_j \phi_j(s)\) with
-a simple root \(\alpha \in \left(0, 1\right]\) has root condition number
-\begin{equation}
-\kappa_{\alpha} =
-  \frac{1}{\alpha \left|p'(\alpha)\right|} \sum_{j = 0}^n \left|
-  b_j \phi_j(\alpha)\right| = \frac{\widetilde{p}(\alpha)}{
-  \alpha \left|p'(\alpha)\right|}.
-\end{equation}
-For the intersection of a degree \(m\) curve \(b_1(s)\) and
-a degree \(n\) curve \(b_2(t)\), we have basis functions
+Since \(F(s, t) = b_0(s) - b_1(t)\) we have Jacobian \(J(s, t) =
+\left[ \begin{array}{c c} b_0'(s) & -b_1'(t) \end{array}\right]\). Since
+a transversal intersection, we have
+\(\det J(\alpha, \beta) \neq 0\). In a perturbation, we replace each
+\(c_j^{(k)}\) with a \(\delta_j^{(k)}\) bounded by
+\(\left|\delta_j^{(k)}\right| \leq \eps \left|c_j^{(k)}\right|\).
+Writing \(J^{-1} = \left[ \begin{array}{c c}
+\bm{v} & \bm{w} \end{array}\right]\), we have
 \begin{multline}
-\phi_{0, -1, 1} = \left[ \begin{array}{c} B_{0, m}(s) \\ 0 \end{array}\right],
-\phi_{0, -1, 2} = \left[ \begin{array}{c} 0 \\ B_{0, m}(s) \end{array}\right],
-\cdots, \\
-\phi_{m, -1, 1} = \left[ \begin{array}{c} B_{m, m}(s) \\ 0 \end{array}\right],
-\phi_{m, -1, 2} = \left[ \begin{array}{c} 0 \\
-  B_{m, m}(s) \end{array}\right], \\
-\phi_{-1, 0, 1} = \left[ \begin{array}{c} -B_{0, n}(t) \\
-  0 \end{array}\right],
-\phi_{-1, 0, 2} = \left[ \begin{array}{c} 0 \\
-  -B_{0, n}(t) \end{array}\right], \cdots, \\
-\phi_{-1, n, 1} = \left[ \begin{array}{c} -B_{n, n}(t) \\
-  0 \end{array}\right], \phi_{-1, n, 2} = \left[ \begin{array}{c} 0 \\
-  -B_{n, n}(t) \end{array}\right].
-\end{multline}
-Since \(F(s, t) = b_1(s) - b_2(t)\) we have Jacobian \(J(s, t) =
-\left[ \begin{array}{c c} b_1'(s) & -b_2'(t) \end{array}\right]\). We'll
-consider a transversal intersection \(F(\alpha, \beta) = \bm{0}\) with
-\(\det J(\alpha, \beta) \neq 0\). Since each of the
-\(\phi_j\) is just a scalar multiple of the standard basis
-vectors, writing \(J^{-1} = \left[ \begin{array}{c c}
-\bm{v}_1 & \bm{v}_2 \end{array}\right]\), we have
-\begin{multline}
-J\left(\alpha, \beta\right)^{-1} \sum_{\bm{j}} \delta_{\bm{j}}
-  \phi_{\bm{j}}\left(\alpha, \beta\right) = \left[\sum_{i = 0}^m
-  \delta_{i, -1, 1} B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
-  \delta_{-1, j, 1} B_{j, n}\left(\beta\right)\right] \bm{v}_1 \\
-+ \left[\sum_{i = 0}^m
-  \delta_{i, -1, 2} B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
-  \delta_{-1, j, 2} B_{j, n}\left(\beta\right)\right] \bm{v}_2 =
-  \nu_1 \bm{v}_1 + \nu_2 \bm{v}_2.
+J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
+  \phi_j\left(\bm{\alpha}\right) =
+  \left[\sum_{i = 0}^m \delta_i^{(1)} B_{i, m}(\alpha) +
+  \sum_{j = 0}^n \delta_j^{(3)} B_{j, n}(\beta)\right] \bm{v} \\
+  + \left[\sum_{i = 0}^m \delta_i^{(2)} B_{i, m}(\alpha) +
+  \sum_{j = 0}^n \delta_j^{(4)} B_{j, n}(\beta)\right] \bm{w} =
+  \nu_1 \bm{v} + \nu_2 \bm{w}
 \end{multline}
 where
-\begin{equation}\label{eq:nu-bounds}
-\left|\nu_k\right| / \eps \leq \sum_{i = 0}^m
-  \left|c_{i, -1, k}\right| B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
-  \left|c_{-1, j, k}\right| B_{j, n}\left(\beta\right) = \mu_k
-\end{equation}
-and the bound can be attained for both \(k = 1, 2\) by making the
-signs of the \(\delta_{\bm{j}}\) agree. If we name the components of each
-curve via
-\(b_1(s) = \left[ \begin{array}{c c} x_1(s) & y_1(s) \end{array}\right]^T\)
-and \(b_2(t) = \left[ \begin{array}{c c} x_2(t) & y_2(t) \end{array}\right]^T\)
-then we see that \(\mu_1 = \widetilde{x}_1(\alpha) + \widetilde{x}_2(\beta)\)
-and \(\mu_2 = \widetilde{y}_1(\alpha) + \widetilde{y}_2(\beta)\).
-Thus we have condition number
+\begin{align}
+\left|\nu_1\right| / \eps &\leq \sum_{i = 0}^m
+  \left|c_{i}^{(1)}\right| B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
+  \left|c_{j}^{(3)}\right| B_{j, n}\left(\beta\right) =
+  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) = \mu_1 \\
+\left|\nu_2\right| / \eps &\leq \sum_{i = 0}^m
+  \left|c_{i}^{(2)}\right| B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
+  \left|c_{j}^{(4)}\right| B_{j, n}\left(\beta\right) =
+  \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta) = \mu_2.
+\end{align}
+As in \eqref{eq:tri-ineq}, the bound can be attained by choosing the
+sign and magnitude of each perturbation so that
+\(\delta_j^{(k)} B_{j, d} = \eps \left|c_j^{(k)}\right| B_{j, d}\).
+The factor of \(\eps\) can be cancelled to give condition number
 \begin{align}
 \kappa_{\alpha, \beta} &= \frac{1}{\sqrt{\alpha^2 + \beta^2}}
-  \max_{\left|\nu_k\right| \leq \mu_k} \left \lVert \nu_1 \bm{v}_1 +
-  \nu_2 \bm{v}_2 \right \rVert_2 \\
+  \sup_{\left|\nu_k\right| \leq \mu_k} \left \lVert \nu_1 \bm{v} +
+  \nu_2 \bm{w} \right \rVert_2 \\
   &=
-  \sqrt{\frac{\max_{\left|\nu_k\right| \leq \mu_k}
-  \nu_1^2 \left(\bm{v}_1 \cdot \bm{v}_1\right) +
-  2 \nu_1 \nu_2 \left(\bm{v}_1 \cdot \bm{v}_2\right) +
-  \nu_2^2 \left(\bm{v}_2 \cdot \bm{v}_2\right)}{\alpha^2 + \beta^2}}
+  \sqrt{\frac{\sup_{\left|\nu_k\right| \leq \mu_k}
+  \nu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
+  2 \nu_1 \nu_2 \left(\bm{v} \cdot \bm{w}\right) +
+  \nu_2^2 \left(\bm{w} \cdot \bm{w}\right)}{\alpha^2 + \beta^2}}
   \label{eq:intersect-cond-num}.
 \end{align}
-Since \(J^{-1}\) is invertible, we know \(\bm{v}_1\) and \(\bm{v}_2\) are
-not parallel which can be used to show that the only internal critical
-point of the function to be maximimized in~\eqref{eq:intersect-cond-num}
-is \(\nu_1 = \nu_2 = 0\), which is the global minimum. Along the boundary of
-the rectangle
-\(\left[-\mu_1, \mu_1\right] \times \left[-\mu_2, \mu_2\right]\),
+Now we seek to maximize the objective function \(\theta(\nu_1, \nu_2) =
+\nu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
+2 \nu_1 \nu_2 \left(\bm{v} \cdot \bm{w}\right) +
+\nu_2^2 \left(\bm{w} \cdot \bm{w}\right)\) in the rectangle
+\(\left[-\mu_1, \mu_1\right] \times \left[-\mu_2, \mu_2\right]\).
+
+To find interior critical points, we solve the system \(\theta_{\nu_1} =
+\theta_{\nu_2} = 0\):
+\begin{equation}
+\left[ \begin{array}{c c}
+  2 \bm{v} \cdot \bm{v} & 2 \bm{v} \cdot \bm{w} \\
+  2 \bm{v} \cdot \bm{w} & 2 \bm{w} \cdot \bm{w} \end{array}\right]
+\left[ \begin{array}{c} \nu_1 \\ \nu_2 \end{array}\right] =
+\left[ \begin{array}{c} 0 \\ 0 \end{array}\right].
+\end{equation}
+This system has the unique solution \(\nu_1 = \nu_2 = 0\) unless
+\(\|\bm{v}\|_2 \|\bm{w}\|_2 = \left|\bm{v} \cdot \bm{w}\right|\).
+By the Cauchy-Schwarz inequality, this can only occur if \(\bm{v}\) and
+\(\bm{w}\) are parallel; since \(J^{-1}\) is invertible, we know they
+are not. Hence \(\theta(0, 0) = 0\) is the only interior critical point and
+it is the global minimum.
+
+Along the boundary of the rectangle,
 we fix one of \(\nu_1\) or \(\nu_2\) and the resulting univariate function is
-an up-opening parabola, hence any critical point must be a local
-minimum. Thus we know the maximum occurs at two of the four corners of the
-rectangle:
+an up-opening parabola. For example, fixing \(\nu_2 = c\) gives
+\(\theta(\nu_1, c) =
+\nu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
+\nu_1\left[2 c \left(\bm{v} \cdot \bm{w}\right)\right] +
+c^2 \left(\bm{w} \cdot \bm{w}\right)\) which has positive lead coefficient
+\(\|\bm{v}\|_2^2\). The lead coefficient cannot be \(0\) since if \(\bm{v}\)
+were the zero vector we'd have \(\det J = 0\).
+Since \(\theta\) is an up-opening parabola along the boundary, any critical
+point must be a local minimum.
+
+Thus we know the maximum occurs at two of the four corners of the
+rectangle. Due to sign cancellation, this leads to one of two values
+\(\theta =
+\mu_1^2 \left(\bm{v} \cdot \bm{v}\right) \pm
+2 \mu_1 \mu_2 \left(\bm{v} \cdot \bm{w}\right) +
+\mu_2^2 \left(\bm{w} \cdot \bm{w}\right)\), the largest of which is
+\(\mu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
+2 \mu_1 \mu_2 \left|\bm{v} \cdot \bm{w}\right| +
+\mu_2^2 \left(\bm{w} \cdot \bm{w}\right)\). Thus
 \begin{equation}\label{eq:intersect-cond-num-too}
 \kappa_{\alpha, \beta} = \sqrt{\frac{\mu_1^2
-  \left(\bm{v}_1 \cdot \bm{v}_1\right) +
-  2 \mu_1 \mu_2 \left|\bm{v}_1 \cdot \bm{v}_2\right| +
-  \mu_2^2 \left(\bm{v}_2 \cdot \bm{v}_2\right)}{\alpha^2 + \beta^2}}.
+  \left(\bm{v} \cdot \bm{v}\right) +
+  2 \mu_1 \mu_2 \left|\bm{v} \cdot \bm{w}\right| +
+  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}{\alpha^2 + \beta^2}}.
 \end{equation}
+Note that \(\widetilde{F}_{\pm} = \left[ \begin{array}{c} \mu_1 \\ \pm \mu_2
+\end{array}\right]\), so
+\begin{equation}
+\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{\pm}
+  \right \rVert_2 = \left \lVert \left[ \begin{array}{c c} \bm{v} & \bm{w}
+  \end{array}\right] \widetilde{F}_{\pm} \right \rVert_2 =
+  \sqrt{\mu_1^2 \left(\bm{v} \cdot \bm{v}\right) \pm
+  2 \mu_1 \mu_2 \left(\bm{v} \cdot \bm{w}\right) +
+  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}
+\end{equation}
+gives each of the two values that produce the maximum value.
+\end{proof}
 
-As far as the author can tell,
-a condition number for the intersection of two planar B\'{e}zier curves
-has not been described in the Computer Aided Geometric Design (CAGD)
-literature. In \cite[Chapter~25, Equation 25.11]{Higham2002}
-a more generic condition number is defined for the root of a nonlinear
-algebraic system that is similar to the definition above.
+\subsection{Transversal Intersection}
 
-For an example, consider the line
-\(b_1(s) = \left[ \begin{array}{c c} 2s & 2s \end{array}\right]^T\)
+Consider the line
+\(b_0(s) = \left[ \begin{array}{c} 2s \\ 2s \end{array}\right]\)
 and improperly parameterized line
-\(b_2(t) = \left[ \begin{array}{c c} 4t^2 & 2 - 4t^2
-\end{array}\right]^T\) which intersect at \(\alpha = \beta = 1/2\).
+\(b_1(t) = \left[ \begin{array}{c} 4t^2 \\ 2 - 4t^2
+\end{array}\right]\) which intersect at \(\alpha = \beta = 1/2\).
 At the intersection we have \(J^{-1} = \frac{1}{8}
 \left[ \begin{array}{c c} 2 & 2 \\ -1 & 1 \end{array}\right]\),
-so that \(\bm{v}_1 \cdot \bm{v}_1 = \bm{v}_2 \cdot \bm{v}_2 =
-5/64\) and \(\bm{v}_1 \cdot \bm{v}_2 = 3/64\). Since the
+so that \(\bm{v} \cdot \bm{v} = \bm{w} \cdot \bm{w} =
+5/64\) and \(\bm{v} \cdot \bm{w} = 3/64\). Since the
 \(x\)-component of \(F(s, t)\) can be written as
@@
 \(\kappa_{\alpha, \beta} = \sqrt{202}/8 \approx 1.78\).
+This low condition number is somewhat unexpected since when using
+the resultant to eliminate each parameter, one of the two roots is
+a double root:
+\begin{align}
+\operatorname{Res}_t\left(x_0(s) - x_1(t), y_0(s) - y_1(t)\right) &=
+  64(2s - 1)^2 \\
+\operatorname{Res}_s\left(x_0(s) - x_1(t), y_0(s) - y_1(t)\right) &=
+  4(2t - 1)(2t + 1).
+\end{align}
+
+\subsection{Line-line Intersection with Poorly Behaved Coefficients}
+
+Consider the intersection of the lines \(y = x\) and \(y = 1 - x\) when
+\(x \in \left[0, 1\right]\). These correspond to the B\'{e}zier curves
+\begin{equation}
+b_0(s) = \left[ \begin{array}{c} s \\ s \end{array}\right], \quad
+b_1(t) = \left[ \begin{array}{c} t \\ 1 - t \end{array}\right].
+\end{equation}
+By adding a scalar \(D > 0\) to each component, we leave \(F(s, t)\) and hence
+the solution unchanged. However, the coefficients of the curves change:
+\begin{equation}
+b_0(s) = \left[ \begin{array}{c} D(1 - s) + (1 + D)s \\ D(1 - s) + (1 + D)s
+  \end{array}\right], \quad b_1(t) = \left[ \begin{array}{c}
+  D(1 - t) + (1 + D)t \\ (1 + D)(1 - t) + Dt \end{array}\right].
+\end{equation}
+At the solution \(\alpha = \beta = 1/2\), we have
+\begin{equation}
+\widetilde{F}_{\pm} = \left[ \begin{array}{c} 2D + 1 \\ \pm(2D + 1)
+  \end{array}\right]
+\end{equation}
+and in either case \(\left \lVert J^{-1} \widetilde{F}_{\pm} \right \rVert_2 =
+2D + 1\).
+
+So, we see the condition number \(\kappa_{\alpha, \beta} = \sqrt{2}(2D + 1)\)
+increases towards infinity as \(D\) does. This is what we expect as the
+coefficients grow so large that their ratio approaches \(1\).
+
+\subsection{Family of Lines Approaching Coincident}
+
+Consider a family of intersections in which one of the lines approaches the
+other:
+\begin{equation}
+b_0(s) = \left[ \begin{array}{c} s \\ 1 \end{array}\right], \quad
+b_1(t) = \left[ \begin{array}{c} t \\ (1 + r)(1 - t) + t \end{array}\right].
+\end{equation}
+These lines \(y = 1\) and \(rx + y = 1 + r\) intersect when
+\(\alpha = \beta = 1\). However as \(r \longrightarrow 0^+\), the lines
+become coincident: if \(r = 0\) the single intersection becomes infinitely
+many.
+
+At the solution, we have \(\widetilde{F}_{\pm} = \left[ \begin{array}{c c}
+2 & \pm 2 \end{array}\right]^T\)
+and again have a condition number
+\begin{equation}
+\kappa_{\alpha, \beta} = \sqrt{\frac{4}{r^2} + \frac{4}{r} + 2} =
+  \frac{2}{r} + 1 + \frac{r}{4} + \bigO{r^2}.
+\end{equation}
+that increases towards infinity as the parameter \(r \longrightarrow 0^+\).
 

### 2018-08-18 nox.py
Updating the extensions to delete for `build_tex`.

@@ -78,5 +78,5 @@ def build_tex(session):
         session,
         "paper",
         "608646FC6AEA50B9AB4A218D45189E6A",
-        extensions=(),
+        extensions=("aux", "bbl", "blg", "log", "out", "toc"),
     )

### 2019-04-07 noxfile.py
Updating to `nox` (from `nox-automation`).
In the process, re-ran `nox -s build_tex` on a new OS (Ubuntu 18.04,
previous was Ubuntu 16.04). This resulted in a small change in the
metadata of `paper.pdf` where `Producer(pdfTeX-1.40.16)` became
`pdfTeX-1.40.18`, the pdfTeX version changed from
`3.14159265-2.6-1.40.16 (TeX Live 2015/Debian)` to
`3.14159265-2.6-1.40.18 (TeX Live 2017/Debian)` and `kpathsea` went
from version `6.2.1` to `6.2.3`.

@@ -23,7 +23,6 @@ import py.path
 
 
 NOX_DIR = os.path.abspath(os.path.dirname(__file__))
-SINGLE_INTERP = "python3.7"
 
 
 def get_path(*names):
@@ -59,18 +58,13 @@ def build_tex_file(session, base, new_id, extensions=()):
     session.run("python", modify_id, "--base", path, "--id", new_id)
 
 
-@nox.session
+@nox.session(py=False)
 def build_tex(session):
-    session.interpreter = SINGLE_INTERP
-
     if py.path.local.sysfind("pdflatex") is None:
         session.skip("`pdflatex` must be installed")
 
     if py.path.local.sysfind("bibtex") is None:
         session.skip("`bibtex` must be installed")
-
-    # No need to create a virtualenv.
-    session.virtualenv = False
 
     session.chdir(get_path("doc"))
 

### 2019-04-07 doc/paper.tex
Putting paper in `elsarticle` format.
Also adding

- "Conclusion and Future Work" section
- "Acknowledgements" section
- Adding a "Condition Number in Practice" section name for the 3
  examples that were previously included in the section
  "Conditioning of Bezier Curve Intersection"
- Slight change in wording about "one of the four corners"

@@
-\documentclass[letterpaper,10pt]{article}
-
-\usepackage[margin=1in]{geometry}
+\documentclass[3p, authoryear, square]{elsarticle}
+\bibliographystyle{elsarticle-harv}
 
@@
 \counterwithin{equation}{section}
-%% H/T: https://tex.stackexchange.com/a/71153/32270
-\usepackage[nottoc,notlot,notlof]{tocbibind}
+%% H/T: https://tex.stackexchange.com/a/26348/32270
+\renewcommand*{\appendixname}{}
+%% H/T: https://tex.stackexchange.com/a/23242/32270
+\renewcommand*{\today}{April 7, 2019}
 
@@
   colorlinks=true,
-  urlcolor=blue,
-  linkcolor=MidnightBlue,
-  citecolor=ForestGreen,
   pdfinfo={
@@
 
-\usepackage{embedfile}
-\embedfile{\jobname.tex}
-
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\lhead{A 2-Norm Condition Number for B\'{e}zier Curve Intersection}
-\rhead{Danny Hermes}
-
-\renewcommand{\headrulewidth}{0pt}
 \renewcommand{\qed}{\(\blacksquare\)}
@@
 
+\journal{Computer Aided Geometric Design}
+
 \begin{document}
+%% H/T: https://tex.stackexchange.com/a/263503/32270
+\hypersetup{
+  urlcolor=MidnightBlue,
+  linkcolor=MidnightBlue,
+  citecolor=ForestGreen,
+}
+
+\begin{frontmatter}
+
+\title{A 2-Norm Condition Number for B\'{e}zier Curve Intersection}
+\author[djh]{Danny Hermes}\ead{dhermes@berkeley.edu}
+\address[djh]{UC Berkeley, 970 Evans Hall \#3840, Berkeley, CA 94720-3840 USA}
 
 \begin{abstract}
-\noindent We present a short note describing a condition number
+We present a short note describing a condition number
 of the intersection of two B\'{e}zier curves.
-\\ \\
-\noindent \emph{Keywords}: B\'{e}zier curve, Curve intersection,
-Condition number, Numerical analysis
 \end{abstract}
 
-\tableofcontents
+\begin{keyword}
+B\'{e}zier curve \sep Curve intersection \sep Condition number \sep
+Numerical analysis
+\end{keyword}
+
+\end{frontmatter}
 
@@
 
-\section{Conditioning of Generic Root-finding}
+\section{Conditioning of Generic Root-finding}\label{sec:generic}
 
@@
 
-Thus we know the maximum occurs at two of the four corners of the
+Thus we know the maximum occurs at one of the four corners of the
 rectangle. Due to sign cancellation, this leads to one of two values
@@
 \end{equation}
-gives each of the two values that produce the maximum value.
+gives each of the two values that could produce the maximum value.
 \end{proof}
+
+\section{Condition Number in Practice}
 
@@
 \(\kappa_{\alpha, \beta} = \sqrt{202}/8 \approx 1.78\).
-This low condition number is somewhat unexpected since when using
-the resultant to eliminate each parameter, one of the two roots is
+This low condition number is expected from a geometric point of view; i.e.
+the intersection is a transversal intersection of two lines. However,
+when using the resultant to eliminate each parameter, one of the two roots is
 a double root:
@@
 \end{align}
+so an algebraic approach may lead to an incorrect conclusion that the
+intersection is ill-conditioned.
 
@@
 increases towards infinity as \(D\) does. This is what we expect as the
-coefficients grow so large that their ratio approaches \(1\).
+coefficients grow so large that their ratio \((1 + D) / D\) approaches \(1\).
 
@@
 
+\section{Conclusion and Future Work}
+
+The author hopes that this can be useful for evaluating and comparing the
+performance of curve intersection implementations. By establishing a
+straightforward and easy to compute closed form, the condition number can be
+used more often to differentiate between cases where the algorithm or computer
+code is at fault for loss in accuracy and cases where the conditioning of the
+intersection itself is the cause. The framework set forth in
+Section~\ref{sec:generic} can be applied in future work to compute the
+condition number of higher order intersections such as surface-surface
+intersections in \(\reals^3\).
+
+\section{Acknowledgements}
+
+The author would like to thank Professor Tom Sederberg for his useful
+course notes (\cite{SederbergNotes}) that provide a useful introduction to
+intersection methods as well as the survey \cite{Sederberg1986}. Additionally
+\cite{Farouki1987} served as a great baseline when considering conditioning
+of operations on B\'{e}zier Curves.
+
+%% H/T: https://tex.stackexchange.com/a/137379/32270
+\section*{\refname}
 \bibliography{paper}
-\bibliographystyle{alpha}
 

### 2019-04-07 noxfile.py

@@ -72,5 +72,5 @@ def build_tex(session):
         session,
         "paper",
         "608646FC6AEA50B9AB4A218D45189E6A",
-        extensions=("aux", "bbl", "blg", "log", "out", "toc"),
+        extensions=("aux", "bbl", "blg", "log", "out", "spl"),
     )

### 2019-06-13 doc/paper.tex
Copy edits based on reviewer feedback.
- Removing "short note" from abstract.
- Changing wording in definition of a Bezier curve.
- Removing "set of" from "the set of control points"
- Changing preliminary note about "Bezier curve intersection" to just
  describe an intersection of two generic planar curves
- Change "smooth functions on R^n" to "smooth functions R^n -> R^n"
- Make vector input x bold in G(x, delta)
- Changing references x_delta to x'

@@
 \begin{abstract}
-We present a short note describing a condition number
+We present a condition number
 of the intersection of two B\'{e}zier curves.
@@
 
-Throughout, we'll refer to a \emph{B\'{e}zier curve} as a parametric
+Throughout, we will refer to a parametric polynomial
 plane curve given by
@@
 \end{equation}
+as a \emph{B\'{e}zier curve},
 where \(B_{j, n}(s) = \binom{n}{j} (1 - s)^{n - j} s^j\) is a Bernstein
@@
 \(B_{j, n}(s) \in \left[0, 1\right]\) as well and the evaluation is a convex
-combination of the set of \emph{control points} \(\bm{b}_j \in \reals^2\).
+combination of the \emph{control points} \(\bm{b}_j \in \reals^2\).
 
-A B\'{e}zier curve intersection is a root \(\left[\begin{array}{c}
+An intersection of two planar curves \(b_0(s)\) and \(b_1(t)\) corresponds to
+a root \(\left[\begin{array}{c}
 \alpha \\ \beta \end{array}\right]\) of the function
 \begin{equation}
-F(s, t) = b_0(s) - b_1(t)
+F(s, t) = b_0(s) - b_1(t).
 \end{equation}
-where \(b_0(s)\) and \(b_1(t)\) are B\'{e}zier curves. Note that
+Note that
 \(F: \reals^2 \longrightarrow \reals^2\).
@@
 \phi_j\left(\bm{x}\right)\) where the basis
-functions \(\phi_j\) are also smooth functions on \(\reals^n\)
+functions \(\phi_j\) are also smooth functions
+\(\reals^n \longrightarrow \reals^n\)
 and each \(c_j \in \reals\). We want to consider the effects on a root
@@
 \begin{equation}
-G(x, \delta) = F\left(\bm{x}\right) + \delta \phi_j\left(\bm{x}\right).
+G\left(\bm{x}, \delta\right) = F\left(\bm{x}\right) +
+\delta \phi_j\left(\bm{x}\right).
 \end{equation}
@@
 Taking the derivative with respect to \(\delta\) we find that
-\(\bm{0} = G_{\bm{x}} \bm{x}_{\delta} + G_{\delta}\). Plugging in
-\(\delta = 0\) we find that \(0 = J\left(\bm{\alpha}\right) \bm{x}_{\delta} +
+\(\bm{0} = G_{\bm{x}} \bm{x}' + G_{\delta}\). Plugging in
+\(\delta = 0\) we find that \(0 = J\left(\bm{\alpha}\right) \bm{x}' +
 \phi_j\left(\bm{\alpha}\right)\), hence we

### 2019-06-13 doc/paper.tex
(Second round of) copy edits based on reviewer feedback.
- Moving inverse from `J(a)^-1` to `J^-1(a)`
- Removing `{}` around description of coefficients `{c_j}`
- Provided a definition for F_c in reference to Higham

@@
 \begin{equation}
-\bm{x}\left(\delta\right) = \bm{\alpha} - J\left(\bm{\alpha}\right)^{-1}
+\bm{x}\left(\delta\right) = \bm{\alpha} - J^{-1}\left(\bm{\alpha}\right)
   \phi_j\left(\bm{\alpha}\right) \delta + \bigO{\delta^2}.
@@
 \phi_j\left(\bm{x}\right)\) parameterized by the coefficients
-\(\left\{c_j\right\}\) with root \(\bm{\alpha}\) and Jacobian
+\(c_j\) with root \(\bm{\alpha}\) and Jacobian
 \(J\left(\bm{\alpha}\right)\), we define a relative root condition
@@
 \end{equation}
+where \(F_{\bm{c}} = \left[\begin{array}{c c c}
+\phi_0\left(\bm{\alpha}\right) & \cdots & \phi_n\left(\bm{\alpha}\right)
+\end{array}\right]^T\) is the vector of weight functions.
 While this has the benefit of having a closed form that is straightforward

### 2019-06-13 doc/paper.tex
Adding a Farouki book to bibliography
Title: Pythagorean-Hodograph Curves: Algebra and Geometry Inseparable

The reviewer pointed out that this is a useful reference for the common
polynomial root condition number.

Also updating the "agrees with common definition" remark about
root condition number of polynomial roots in the `n = 1` case.
(Third round of) copy edits based on reviewer feedback.
- Changing "be degree" to "be of degree" when describing a polynomial
  degree
- Changing "Since a transversal intersection" to "Since we are
  considering a transversal intersection"
- Adding "the rela

@@
 \end{equation}
-that agrees with the common definition (\cite{Farouki1987}) when the
-\(\phi_j\) are specialized to Bernstein basis functions.
+that agrees with the common definition
+(\cite[Equation~12.33]{Farouki2008}) for any polynomial basis
+\(\phi_j\).
 
@@
 greater of two vector norms:
-\begin{equation}
+\begin{equation}\label{eq:kappa-max}
 \kappa_{\alpha, \beta} = \frac{1}{\sqrt{\alpha^2 + \beta^2}} \max \left\{
@@
 \begin{proof}
-Let the curve \(b_0(s)\) be degree \(m\) and \(b_1(t)\) be degree \(n\).
-Then \(F(s, t)\) can be written as \(2(m + 1) + 2(n + 1)\) terms:
+Let the curve \(b_0(s)\) be of degree \(m\) and \(b_1(t)\) be of degree \(n\).
+Then \(F(s, t)\) can be written as \\ \(2(m + 1) + 2(n + 1)\) terms:
 \begin{equation}
@@
 Since \(F(s, t) = b_0(s) - b_1(t)\) we have Jacobian \(J(s, t) =
-\left[ \begin{array}{c c} b_0'(s) & -b_1'(t) \end{array}\right]\). Since
-a transversal intersection, we have
+\left[ \begin{array}{c c} b_0'(s) & -b_1'(t) \end{array}\right]\). Since we
+are considering a transversal intersection, we have
 \(\det J(\alpha, \beta) \neq 0\). In a perturbation, we replace each
@@
 \(\delta_j^{(k)} B_{j, d} = \eps \left|c_j^{(k)}\right| B_{j, d}\).
-The factor of \(\eps\) can be cancelled to give condition number
+The factor of \(\eps\) can be cancelled to give the relative root
+condition number
 \begin{align}
@@
 \end{equation}
-gives each of the two values that could produce the maximum value.
+gives both values of which we take the maximum in \eqref{eq:kappa-max}.
 \end{proof}
@@
 \(b_0(s) = \left[ \begin{array}{c} 2s \\ 2s \end{array}\right]\)
-and improperly parameterized line
+and quadratically parameterized line
 \(b_1(t) = \left[ \begin{array}{c} 4t^2 \\ 2 - 4t^2
@@
 \begin{equation}
-b_0(s) = \left[ \begin{array}{c} s \\ s \end{array}\right], \quad
-b_1(t) = \left[ \begin{array}{c} t \\ 1 - t \end{array}\right].
+b_0(s) = s \left[ \begin{array}{c} 1 \\ 1 \end{array}\right], \quad
+b_1(t) = (1 - t) \left[ \begin{array}{c} 0 \\ 1 \end{array}\right] +
+t \left[ \begin{array}{c} 1 \\ 0 \end{array}\right].
 \end{equation}
@@
 \cite{Farouki1987} served as a great baseline when considering conditioning
-of operations on B\'{e}zier Curves.
+of operations on B\'{e}zier curves.
 

### 2019-06-13 doc/paper.tex
Adding clarification on xtilde and ytilde in Theorem 4.1.

@@
 the (absolute) condition number of evaluation is
-\(\widetilde{p}(s) = \sum_{j = 0}^n \left|p_j\right| B_{j, n}(s)\)
+\begin{equation}\label{eq:p-tilde}
+\widetilde{p}(s) = \sum_{j = 0}^n \left|p_j\right| B_{j, n}(s)
+\end{equation}
 (\cite{Farouki1987}) when the parameter \(s\) is in the unit interval.
@@
 \end{equation}
+where the \(\widetilde{x}_i, \widetilde{y}_j\) are as defined in
+\eqref{eq:p-tilde}.
 Then the root condition number of the intersection is the

### 2019-06-17 doc/paper.tex
Replacing **all** J(...)^{-1} with J^{-1}(...).
I.e. I moved the position of the inverse.
Emphasizing (in 3.10) that Ftilde is in the condition number.
Expanding on discussion of the Higham condition number.
This is in preparation to show that the Higham condition number
is larger than the one we propose.

@@
 \begin{equation}
-\frac{\left \lVert J\left(\bm{\alpha}\right)^{-1}
+\frac{\left \lVert J^{-1}\left(\bm{\alpha}\right)
   \phi_j\left(\bm{\alpha}\right) \right \rVert}{
@@
 \bm{x}\left(\delta_0, \ldots, \delta_n\right) = \bm{\alpha} -
-  J\left(\bm{\alpha}\right)^{-1} \sum_{j = 0}^n \delta_j
+  J^{-1}\left(\bm{\alpha}\right) \sum_{j = 0}^n \delta_j
   \phi_j\left(\bm{\alpha}\right) + \bigO{\eps^2}.
@@
   \eps \left|c_j\right|} \frac{\left \lVert
-  J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
+  J^{-1}\left(\bm{\alpha}\right) \sum_j \delta_j
   \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
@@
 given. Instead of bounding the perturbations component-wise, it bounds
-the entire perturbation vector
+the entire perturbation vector \(\bm{\delta}\)
 \begin{equation}
@@
   \eps \left \lVert \bm{c} \right \rVert} \frac{\left \lVert
-  J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
+  J^{-1}\left(\bm{\alpha}\right) \sum_j \delta_j
   \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
-  \left \lVert \bm{\alpha} \right \rVert}\right) =
-  \left \lVert J^{-1} F_{\bm{c}} \right \rVert \frac{\left \lVert \bm{c}
-  \right \rVert}{\left \lVert \bm{\alpha} \right \rVert}.
+  \left \lVert \bm{\alpha} \right \rVert}\right).
 \end{equation}
-where \(F_{\bm{c}} = \left[\begin{array}{c c c}
-\phi_0\left(\bm{\alpha}\right) & \cdots & \phi_n\left(\bm{\alpha}\right)
-\end{array}\right]^T\) is the vector of weight functions.
-While this has the benefit of having a closed form that is straightforward
-to compute, it may be less useful than the condition number given in
-Definition~\ref{defn:abstract-cond-num} since the larger coefficients
-can dominate the rest.
+It's possible to rewrite \(\sum_j \delta_j \phi_j\left(\bm{\alpha}\right) =
+F_{\bm{c}} \bm{\delta}\) where \(F_{\bm{c}} =
+\left[\frac{\partial F_i}{\partial c_j}\right]_{ij} =
+\left[\begin{array}{c c c} \phi_0\left(\bm{\alpha}\right) & \cdots &
+\phi_n\left(\bm{\alpha}\right) \end{array}\right]\) is the Jacobian of \(F\)
+with respect to the coefficients \(\bm{c}\). With this representation, the
+Higham condition number has a closed form since
+\begin{equation}
+  \left \lVert
+  J^{-1} F_{\bm{c}} \bm{\delta} \right \rVert / \eps \leq
+  \left \lVert J^{-1} F_{\bm{c}} \right \rVert \left \lVert \bm{\delta} \right
+  \rVert / \eps \leq \left \lVert J^{-1} F_{\bm{c}} \right \rVert \left \lVert
+  \bm{c} \right \rVert
+\end{equation}
+for any matrix norm that is compatible with the vector norm used on
+\(\bm{\delta}\). The Frobenius matrix norm and Euclidean vector norm can be
+combined to give a condition number that is straightforward to compute:
+\begin{equation}
+  \kappa_H = \left \lVert J^{-1} F_{\bm{c}} \right \rVert_F
+  \frac{\left \lVert \bm{c}
+  \right \rVert_2}{\left \lVert \bm{\alpha} \right \rVert_2}.
+\end{equation}
+
+While this closed form for \(\kappa_H\) is useful, it provides a less sharp
+measure than the condition number \(\kappa_{\bm{\alpha}}\) given in
+Definition~\ref{defn:abstract-cond-num} since the ball \(\left \lVert
+\bm{\delta} \right \rVert_2 \leq \eps \left \lVert \bm{c} \right \rVert_2\)
+can allow larger perturbations of a single coefficient than the box determined
+by \(\left|\delta_j\right| \leq \eps \left|c_j\right|\) and allows
+perturbations in zero coefficients.
+When specialized to planar B\'{e}zier curves, we'll show in
+Theorem~\ref{thm:kappa-closed-form} that \(\kappa_{\alpha}\) has a closed form
+as well\footnote{When the Euclidean norm is used}. In addition, this closed
+form shows that \(\kappa_{\alpha}\) is a natural extension of the
+one-dimensional equivalent given in~\eqref{eq:bernstein-cond-num} below.
 
@@
 Thus we get a root condition number for a polynomial given in Bernstein form
-\begin{equation}
+\begin{equation}\label{eq:bernstein-cond-num}
 \kappa_{\alpha} =
   \frac{1}{\left|\alpha F'(\alpha)\right|} \sum_{j = 0}^n \left|
-  c_j \phi_j(\alpha)\right|.
+  c_j \phi_j(\alpha)\right| =
+  \frac{\widetilde{F}(\alpha)}{\left|\alpha F'(\alpha)\right|}
 \end{equation}
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:kappa-closed-form}
 Let \(\left[\begin{array}{c} \alpha \\ \beta
@@
 \kappa_{\alpha, \beta} = \frac{1}{\sqrt{\alpha^2 + \beta^2}} \max \left\{
-\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{+}\right \rVert_2,
-\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{-}\right \rVert_2
+\left \lVert J^{-1}\left(\alpha, \beta\right) \widetilde{F}_{+}\right \rVert_2,
+\left \lVert J^{-1}\left(\alpha, \beta\right) \widetilde{F}_{-}\right \rVert_2
 \right\}.
@@
 \begin{multline}
-J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
+J^{-1}\left(\bm{\alpha}\right) \sum_j \delta_j
   \phi_j\left(\bm{\alpha}\right) =
@@
 \begin{equation}
-\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{\pm}
+\left \lVert J^{-1}\left(\alpha, \beta\right) \widetilde{F}_{\pm}
   \right \rVert_2 = \left \lVert \left[ \begin{array}{c c} \bm{v} & \bm{w}

### 2019-06-17 doc/paper.tex
Moving coefficients to the RHS of vectors in eqn 5.5.
Re-working Theorem 4.1 statement to emphasize the computation.
The "max" was an unnecessary redirection.

@@
 \begin{theorem}\label{thm:kappa-closed-form}
-Let \(\left[\begin{array}{c} \alpha \\ \beta
-\end{array}\right]\) be a transversal intersection of two planar
-B\'{e}zier curves \(b_0(s)\) and \(b_1(t)\). Define the vectors
+Let \(\left[\begin{array}{c} \alpha \\ \beta \end{array}\right]\) be a
+transversal intersection of two planar B\'{e}zier curves \(b_0(s)\) and
+\(b_1(t)\). Then the root condition number of the intersection is
+\begin{equation}\label{eq:kappa-max}
+\kappa_{\alpha, \beta} = \sqrt{\frac{\mu_1^2
+  \left(\bm{v} \cdot \bm{v}\right) +
+  2 \mu_1 \mu_2 \left|\bm{v} \cdot \bm{w}\right| +
+  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}{\alpha^2 + \beta^2}}
+\end{equation}
+where
 \begin{equation}
-\widetilde{F}_{+} = \left[ \begin{array}{c}
-  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
-  \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta) \end{array}\right] \quad
-\text{and} \quad
-\widetilde{F}_{-} = \left[ \begin{array}{c}
-  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
-  -\widetilde{y}_0(\alpha) - \widetilde{y}_1(\beta)\end{array}\right].
+  J^{-1}\left(\alpha, \beta\right) = \left[ \begin{array}{c c}
+  \bm{v} & \bm{w} \end{array}\right] \qquad
+  \mu_1 = \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \qquad
+  \mu_2 = \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta).
 \end{equation}
-where the \(\widetilde{x}_i, \widetilde{y}_j\) are as defined in
+Here \(b_0(s) = \left[\begin{array}{c c} x_0(s) & y_0(s)\end{array}\right]^T\)
+and \(b_1(t) = \left[\begin{array}{c c} x_1(t) & y_1(t)\end{array}\right]^T\)
+and the \(\widetilde{x}_i, \widetilde{y}_j\) are as defined in
 \eqref{eq:p-tilde}.
-Then the root condition number of the intersection is the
-greater of two vector norms:
-\begin{equation}\label{eq:kappa-max}
-\kappa_{\alpha, \beta} = \frac{1}{\sqrt{\alpha^2 + \beta^2}} \max \left\{
-\left \lVert J^{-1}\left(\alpha, \beta\right) \widetilde{F}_{+}\right \rVert_2,
-\left \lVert J^{-1}\left(\alpha, \beta\right) \widetilde{F}_{-}\right \rVert_2
-\right\}.
-\end{equation}
 \end{theorem}
@@
 \(\left|\delta_j^{(k)}\right| \leq \eps \left|c_j^{(k)}\right|\).
-Writing \(J^{-1} = \left[ \begin{array}{c c}
+By writing \(J^{-1} = \left[ \begin{array}{c c}
 \bm{v} & \bm{w} \end{array}\right]\), we have
@@
   2 \mu_1 \mu_2 \left|\bm{v} \cdot \bm{w}\right| +
-  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}{\alpha^2 + \beta^2}}.
+  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}{\alpha^2 + \beta^2}}
 \end{equation}
-Note that \(\widetilde{F}_{\pm} = \left[ \begin{array}{c} \mu_1 \\ \pm \mu_2
-\end{array}\right]\), so
-\begin{equation}
-\left \lVert J^{-1}\left(\alpha, \beta\right) \widetilde{F}_{\pm}
-  \right \rVert_2 = \left \lVert \left[ \begin{array}{c c} \bm{v} & \bm{w}
-  \end{array}\right] \widetilde{F}_{\pm} \right \rVert_2 =
-  \sqrt{\mu_1^2 \left(\bm{v} \cdot \bm{v}\right) \pm
-  2 \mu_1 \mu_2 \left(\bm{v} \cdot \bm{w}\right) +
-  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}
-\end{equation}
-gives both values of which we take the maximum in \eqref{eq:kappa-max}.
+as desired.
 \end{proof}
@@
 \begin{equation}
-b_0(s) = s \left[ \begin{array}{c} 1 \\ 1 \end{array}\right], \quad
-b_1(t) = (1 - t) \left[ \begin{array}{c} 0 \\ 1 \end{array}\right] +
-t \left[ \begin{array}{c} 1 \\ 0 \end{array}\right].
+b_0(s) = \left[ \begin{array}{c} 1 \\ 1 \end{array}\right] s, \quad
+b_1(t) = \left[ \begin{array}{c} 0 \\ 1 \end{array}\right] (1 - t) +
+\left[ \begin{array}{c} 1 \\ 0 \end{array}\right] t.
 \end{equation}

### 2019-06-17 doc/paper.tex
Updating references to F_{+/-} based on recent change to theorem 4.1.

@@
 \end{equation}
-At the solution \(\alpha = \beta = 1/2\), we have
+At the solution \(\alpha = \beta = 1/2\), we have \(\mu_1 = \mu_2 = 2D + 1\)
+and
 \begin{equation}
-\widetilde{F}_{\pm} = \left[ \begin{array}{c} 2D + 1 \\ \pm(2D + 1)
-  \end{array}\right]
+J^{-1} = \frac{1}{2}
+\left[ \begin{array}{c c} 1 & 1 \\ -1 & 1 \end{array}\right]
 \end{equation}
-and in either case \(\left \lVert J^{-1} \widetilde{F}_{\pm} \right \rVert_2 =
-2D + 1\).
-
+so that \(\bm{v} \cdot \bm{v} = \bm{w} \cdot \bm{w} =
+1/2\) and \(\bm{v} \cdot \bm{w} = 0\).
 So, we see the condition number \(\kappa_{\alpha, \beta} = \sqrt{2}(2D + 1)\)
@@
 
-At the solution, we have \(\widetilde{F}_{\pm} = \left[ \begin{array}{c c}
-2 & \pm 2 \end{array}\right]^T\)
-and again have a condition number
+At the solution, we have \(\mu_1 = \mu_2 = 2\) and
+\begin{equation}
+J^{-1} = \frac{1}{r}
+\left[ \begin{array}{c c} r & 1 \\ 0 & 1 \end{array}\right]
+\end{equation}
+so that \(\bm{v} \cdot \bm{v} = 1\), \(\bm{v} \cdot \bm{w} =
+1/r\) and \(\bm{w} \cdot \bm{w} = 2/r^2\). Again have a condition number
 \begin{equation}

### 2019-06-17 doc/paper.tex
Added "trivial" example showing equivalence to 1D case.

@@
 combined to give a condition number that is straightforward to compute:
-\begin{equation}
+\begin{equation}\label{eq:higham-cond-num}
   \kappa_H = \left \lVert J^{-1} F_{\bm{c}} \right \rVert_F
@@
 
+\subsection{Collapsing to One-dimensional Case}
+
+One key argument for choosing Definition~\ref{defn:abstract-cond-num} over
+the Highham condition number \(\kappa_H\) from~\eqref{eq:higham-cond-num} is
+that \(\kappa_{\bm{\alpha}}\) is a natural extension of the condition number
+for the equivalent one-dimensional problem. To see that this is so, we'll
+define a "trivial" example by starting with a polynomial \(p(s)\) in Bernstein
+form and a simple root \(\alpha\).
+
+We define the B\'{e}zier curves \(b_0(s) = \left[ \begin{array}{c} p(s) \\ 0
+\end{array}\right]\) and \(b_1(t) = \left[ \begin{array}{c} 0 \\ t
+\end{array}\right]\). These curves intersect when \(\beta = 0\) and
+\(\alpha\) is a root of \(p(s)\).
+At such an intersection \(\mu_1 = \widetilde{p}(\alpha) + 0\),
+\(\mu_2 = 0 + \beta = 0\) and
+\begin{equation}
+J^{-1} = \left[ \begin{array}{c c} 1 / p'(\alpha) & 0 \\ 0 & -1 \end{array}\right]
+\end{equation}
+so that \(\bm{v} \cdot \bm{v} = 1 / \left[p'(\alpha)\right]^2\), \(\bm{v} \cdot
+\bm{w} = 0\) and \(\bm{w} \cdot \bm{w} = 1\). This produces
+\begin{equation}
+  \kappa_{\alpha, 0} = \sqrt{\frac{\mu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
+  0 + 0}{\alpha^2 + 0}} = \frac{\widetilde{p}(\alpha)}{\left|\alpha
+  p'(\alpha)\right|},
+\end{equation}
+the commonly used condition number presented
+in~\eqref{eq:bernstein-cond-num}.
+
 \subsection{Line-line Intersection with Poorly Behaved Coefficients}

### 2019-06-17 doc/paper.tex
Replacing "Euclidean norm" with 2-norm.
This is to agree with the title and other usage throughout.

@@
 for any matrix norm that is compatible with the vector norm used on
-\(\bm{\delta}\). The Frobenius matrix norm and Euclidean vector norm can be
+\(\bm{\delta}\). The Frobenius matrix norm and vector 2-norm can be
 combined to give a condition number that is straightforward to compute:
@@
 Theorem~\ref{thm:kappa-closed-form} that \(\kappa_{\alpha}\) has a closed form
-as well\footnote{When the Euclidean norm is used}. In addition, this closed
+as well\footnote{When the 2-norm is used}. In addition, this closed
 form shows that \(\kappa_{\alpha}\) is a natural extension of the

### 2019-06-17 doc/paper.tex
Removing extra "and" from Theorem 4.1.

@@
 \end{equation}
-Here \(b_0(s) = \left[\begin{array}{c c} x_0(s) & y_0(s)\end{array}\right]^T\)
-and \(b_1(t) = \left[\begin{array}{c c} x_1(t) & y_1(t)\end{array}\right]^T\)
+Here \(b_0(s) = \left[\begin{array}{c c} x_0(s) & y_0(s)\end{array}\right]^T\),
+\(b_1(t) = \left[\begin{array}{c c} x_1(t) & y_1(t)\end{array}\right]^T\)
 and the \(\widetilde{x}_i, \widetilde{y}_j\) are as defined in

### 2019-06-18 doc/paper.tex
Tweaking notation / LaTeX double quote in section 5.2.

@@
 the Highham condition number \(\kappa_H\) from~\eqref{eq:higham-cond-num} is
-that \(\kappa_{\bm{\alpha}}\) is a natural extension of the condition number
+that \(\kappa_{\alpha, \beta}\) is a natural extension of the condition number
 for the equivalent one-dimensional problem. To see that this is so, we'll
-define a "trivial" example by starting with a polynomial \(p(s)\) in Bernstein
+define a ``trivial" example by starting with a polynomial \(p(s)\) in Bernstein
 form and a simple root \(\alpha\).

### 2019-06-18 doc/paper.tex
Adding note showing that kappa_{a,b} <= kappa_H.

@@
 Then \(F(s, t)\) can be written as \\ \(2(m + 1) + 2(n + 1)\) terms:
-\begin{equation}
+\begin{equation}\label{eq:bezier-full-basis}
 F(s, t) =
@@
 \end{proof}
+
+With this closed form \(\kappa_{\alpha, \beta}\) in hand, we can now compare
+to the Higham condition number \(\kappa_H\) from~\eqref{eq:higham-cond-num}.
+We'll show that \(\kappa_{\alpha, \beta} \leq \kappa_H\) by comparing
+\(\kappa_{\alpha, \beta}^2 \left(\alpha^2 + \beta^2\right)\)
+to \(\kappa_H^2 \left(\alpha^2 + \beta^2\right) = \left \lVert J^{-1}
+F_{\bm{c}} \right \rVert_F^2 \left \lVert \bm{c} \right \rVert_2^2\).
+In the case of planar curves with basis as in~\eqref{eq:bezier-full-basis},
+\begin{equation}
+  \left \lVert J^{-1} F_{\bm{c}} \right \rVert_F^2 =
+  \left[\left \lVert \bm{v} \right \rVert_2^2 + \left \lVert \bm{w}
+  \right \rVert_2^2 \right] W \quad \text{where} \quad W =
+  \sum_{i = 0}^m B_{i, m}^2(\alpha) + \sum_{j = 0}^n B_{j, n}^2(\beta)
+\end{equation}
+is the sum of squared Bernstein weights.
+With two applications of the Cauchy-Schwarz inequality we know that
+\begin{equation}
+  \kappa_{\alpha, \beta}^2 \left(\alpha^2 + \beta^2\right) \leq
+  \left(\mu_1 \left \lVert \bm{v} \right \rVert_2 + \mu_2 \left \lVert \bm{w}
+  \right \rVert_2\right)^2 \leq \left(\mu_1^2 + \mu_2^2\right) \left[
+  \left \lVert \bm{v} \right \rVert_2^2 + \left \lVert \bm{w}
+  \right \rVert_2^2 \right].
+\end{equation}
+So it remains to show that \(\mu_1^2 + \mu_2^2 \leq W \left \lVert \bm{c}
+\right \rVert_2^2\), which can be done with another application of
+Cauchy-Schwarz to the terms in \(\mu_1\) and \(\mu_2\):
+\begin{equation}
+  \mu_1^2 + \mu_2^2 \leq \left(\sum_{i = 0}^m \left|c_i^{(1)}\right|^2 +
+  \sum_{j = 0}^n \left|c_j^{(3)}\right|^2 \right) W + \left(\sum_{i = 0}^m
+  \left|c_i^{(2)}\right|^2 + \sum_{j = 0}^n \left|c_j^{(4)}\right|^2 \right) W
+  = W \left \lVert \bm{c} \right \rVert_2^2.
+\end{equation}
 

### 2019-10-18 doc/paper.tex
Updates based on 2nd round of review (part 1).
- Replacing " then" with ", " as a pause
- Using bold 0 (i.e. vector) when specializing dG/d(delta) to delta = 0
- Replacing "It's" with "It is"
- Adding "a sum of" to sentence about terms in Theorem 4.1
- Removing "of" from "The factor of epsilon"
- Replacing "we'd" with "we would"
- Using "Coincidence" instead of "Coincident" in section 5.4
  heading
- Adding "we" in "Again we have a condition number"

These changes are only in `paper.tex`, I have avoided checking in
`paper.pdf` until all changes are complete (since a binary file creates
a somew

@@
 Since \(G\left(\bm{\alpha}, 0\right) = \bm{0}\), if \(J^{-1}\) exists at
-\(\bm{x} = \bm{\alpha}\) then
+\(\bm{x} = \bm{\alpha}\),
 the implicit function theorem tells us that we can define
@@
 \(\bm{0} = G_{\bm{x}} \bm{x}' + G_{\delta}\). Plugging in
-\(\delta = 0\) we find that \(0 = J\left(\bm{\alpha}\right) \bm{x}' +
+\(\delta = 0\) we find that \(\bm{0} = J\left(\bm{\alpha}\right) \bm{x}' +
 \phi_j\left(\bm{\alpha}\right)\), hence we
@@
 \end{equation}
-It's possible to rewrite \(\sum_j \delta_j \phi_j\left(\bm{\alpha}\right) =
+It is possible to rewrite \(\sum_j \delta_j \phi_j\left(\bm{\alpha}\right) =
 F_{\bm{c}} \bm{\delta}\) where \(F_{\bm{c}} =
@@
 Let the curve \(b_0(s)\) be of degree \(m\) and \(b_1(t)\) be of degree \(n\).
-Then \(F(s, t)\) can be written as \\ \(2(m + 1) + 2(n + 1)\) terms:
+Then \(F(s, t)\) can be written as a sum of \(2(m + 1) + 2(n + 1)\) terms:
 \begin{equation}\label{eq:bezier-full-basis}
@@
 \(\delta_j^{(k)} B_{j, d} = \eps \left|c_j^{(k)}\right| B_{j, d}\).
-The factor of \(\eps\) can be cancelled to give the relative root
+The factor \(\eps\) can be cancelled to give the relative root
 condition number
@@
 \(\|\bm{v}\|_2^2\). The lead coefficient cannot be \(0\) since if \(\bm{v}\)
-were the zero vector we'd have \(\det J = 0\).
+were the zero vector we would have \(\det J = 0\).
 Since \(\theta\) is an up-opening parabola along the boundary, any critical
@@
 
-\subsection{Family of Lines Approaching Coincident}
+\subsection{Family of Lines Approaching Coincidence}
 
@@
 so that \(\bm{v} \cdot \bm{v} = 1\), \(\bm{v} \cdot \bm{w} =
-1/r\) and \(\bm{w} \cdot \bm{w} = 2/r^2\). Again have a condition number
+1/r\) and \(\bm{w} \cdot \bm{w} = 2/r^2\). Again we have a condition number
 \begin{equation}

### 2019-10-18 doc/paper.tex
Updates based on 2nd round of review (part 3).
Rewording first sentence of Theorem 4.1; making sure to note
that (a, b) is a vector (s, t) where b0(s) = b1(t).

@@
   \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
-  \left \lVert\bm{\alpha}\right \rVert}\right).
+  \left \lVert\bm{\alpha}\right \rVert}\right)
 \end{equation}
+where \(\bm{\alpha} + \delta \bm{\alpha}\) is a root of the perturbed
+function \(\sum_j (c_j + \delta_j) \phi_j\left(\bm{x}\right)\).
 \end{definition}
@@
 \begin{theorem}\label{thm:kappa-closed-form}
-Let \(\left[\begin{array}{c} \alpha \\ \beta \end{array}\right]\) be a
-transversal intersection of two planar B\'{e}zier curves \(b_0(s)\) and
-\(b_1(t)\). Then the root condition number of the intersection is
+Let \(\left[\begin{array}{c} \alpha \\ \beta \end{array}\right]\) be the
+parameter vector \(\left[\begin{array}{c} s \\ t \end{array}\right]\)
+at which two planar B\'{e}zier curves \(b_0(s)\) and \(b_1(t)\)
+have a transversal intersection.
+Then the root condition number of the intersection is
 \begin{equation}\label{eq:kappa-max}
